PHAT RAID, yo

### 2014-05-12 paper/paper.tex
Add supervisor listing and discuss it

\usepackage{titling}
\setlength{\droptitle}{-5em}

@@

>>>>

\usepackage{titling}
% move the title up a bit, wastes less space
\setlength{\droptitle}{-5em}

\usepackage[usenames,dvipsnames]{color}
% for \color used in listings
\usepackage{textcomp}
% for upquote used in listings
\usepackage{listings}
\lstset{
    breakatwhitespace, % somehow prevents lstinline from line splitting
    tabsize=2,
    rulecolor=,
    basicstyle=\footnotesize,
    upquote=true,
    aboveskip={1.5\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    keywordstyle=\color{Purple},
    identifierstyle=\color{Black},
    commentstyle=\color{BrickRed},
    stringstyle=\color{RubineRed},
    captionpos=b,
}
\lstloadlanguages{erlang}
\lstset{language=erlang}

@@

\lstinputlisting[firstline=6,lastline=18,float,
                 caption=Supervisor Behavior --- \texttt{phat.erl},label=supervisor,
                 numbers=left, firstnumber=6]
                {../phat.erl}

Listing \ref{supervisor} is taken from our supervisor code. When a supervisor is
started, the \texttt{supervisor} behavior looks for a unary procedure called
\lstinline!init!. The \lstinline!init! procedure returns a child specification which
is a pair of a restart specification and a list of children. In Listing
\ref{supervisor}, the restart specification, \lstinline!{one_for_all,1,5}!
specifies that if any one node dies, all nodes should be restarted, unless more
than one failure has occurred in the past five seconds. If more than one failure
occurs in five seconds, the supervisor kills all the children and shuts itself
down as well.

Each child in the list of children is a 6-tuple consisting of: child name,
initial procedure call, child transience, shutdown style, child type, necessary
modules.

\begin{itemize}
\item The initial procedure call is a 3-tuple of module, procedure name and
  argument list.
\item Every child's transience is specified as \lstinline!permanent!, meaning
  they should be restarted.
\item Every child has shutdown style \lstinline!1! meaning they will first be
  asked to terminate and one second later they will be forcibly terminated.
\item All of our children are workers, which are distinguished from
  sub-supervisors.
\item The necessary modules are dynamically loaded when the child processes is
  initialized, there is a one-to-one mapping between our children and code
  modules.
\end{itemize}
